Transfer Learning in Visual and Relational Reasoning

### 2019-11-16 cvpr_submission/introduction.tex
Removing other occurences of "compositional".

In this work, we focus on multi-modal learning~\cite{mogadala2019trends} combining vision and language,
and in particular, transfer learning for visual reasoning tasks with a rich logical structure, e.g., see~\cite{johnson2017clevr,yang2018dataset}. 
While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, challenges arise
once the modalities have been fused.
For example, in compositional reasoning problems that involve objects with multiple attributes,
feature representations in the source domain may be entangled and not easily transfer over to the target domain~\cite{johnson2017clevr}.
In video reasoning, an additional challenge in the temporal dimension is whether a model trained on shorter video sequences will 
transfer over to longer sequences~\cite{yang2018dataset,song2018explore}.
To address these challenges, mechanisms such as attention~\cite{bahdanau2014neural} 
and external memory~\cite{graves2014neural, graves2016hybrid,weston2014memory} 
which facilitate higher-level abstractions, seem more promising.

>>>>

In this work, we focus on multi-modal learning~\cite{mogadala2019trends} combining vision and language,
and in particular, transfer learning for visual reasoning tasks with a rich logical structure, e.g., see~\cite{johnson2017clevr,yang2018dataset}. 
While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, challenges arise
once the modalities have been fused.
For example, in visual reasoning problems that involve objects with multiple attributes,
feature representations in the source domain may be entangled and not easily transfer over to the target domain~\cite{johnson2017clevr}.
In video reasoning, an additional challenge in the temporal dimension is whether a model trained on shorter video sequences will 
transfer over to longer sequences~\cite{yang2018dataset,song2018explore}.
To address these challenges, mechanisms such as attention~\cite{bahdanau2014neural} 
and external memory~\cite{graves2014neural, graves2016hybrid,weston2014memory} 
which facilitate higher-level abstractions, seem more promising.

### 2019-11-16 cvpr_submission/related_work.tex
Minor corrections. Add or remove commas, Add \compresslist option for transfer learning section.
Removing other occurences of "compositional".

Another research focus area has been multimodal fusion and attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal features~\cite{zhou2015simple, antol2015}. Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions~\cite{fukui2016multimodal, kim2016hadamard}. Attention research in VQA has demonstrated that learning question-guided visual attention on image regions is the most promising approach~\cite{yang2016stacked, chen2015abc, ilievski2016focused}. Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods~\cite{hudson2018compositional, song2018explore}. Visualization of attention maps also provides interpretability, which is an increasingly important aspect. The MAC model \cite{hudson2018compositional} is a great example of such an approach. The follow-on model by the same authors~\cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.  Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction~\cite{haurilet2019s, teney2017graph, kim2018dynamic}.

Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning. Early works~\cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video. These approaches might be sufficient for action-recognition type of tasks but fall short when spatio-temporal reasoning is required. Learning long-term dependencies is also another challenge that LSTMs may struggle with. Yin et al.~\cite{yin2019memory} recently proposed a Memory-Augmented Neural Network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling long-term visual-textual dependencies.

>>>>

Another research focus area has been multimodal fusion and attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal features~\cite{zhou2015simple, antol2015}. Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions~\cite{fukui2016multimodal, kim2016hadamard}. Attention research in VQA has demonstrated that learning question-guided visual attention on image regions is the most promising approach~\cite{yang2016stacked, chen2015abc, ilievski2016focused}. Visual reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods~\cite{hudson2018compositional, song2018explore}. Visualization of attention maps also provides interpretability, which is an increasingly important aspect. The MAC model \cite{hudson2018compositional} is a great example of such an approach. The follow-on model by the same authors~\cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.  Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction~\cite{haurilet2019s, teney2017graph, kim2018dynamic}.

Video question answering, aside from spatial queries, also focuses on questions that require \emph{temporal} reasoning. Early works~\cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video. These approaches might be sufficient for action-recognition type of tasks but fall short when spatio-temporal reasoning is required. Learning long-term dependencies is also another challenge that LSTMs may struggle with. Yin et al.~\cite{yin2019memory} recently proposed a Memory-Augmented Neural Network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling long-term visual-textual dependencies.
